Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A cross-sectional study based on the parametric g-formula

### 2024-07-21 output/paper/_figures.qmd
Finished addressing comments reviwer 1.
Adapting template docx.

::: {#fig-dag}
```{dot}
//| fig-width: 9
//| fig-height: 10

@@

    node [shape=ellipse]
    U [label='Confounders']

    node [shape=box, height=0.3, width=0.3]
    E [label='EDCs']
    M [label='Glucocorticosteroids']
    Y [label='HRT-SE']
    { rank = same; E M}

>>>>

::: {#fig-dag}
```{dot}
//| fig-width: 4
//| fig-height: 4

@@

    node [shape=ellipse]
    U [label="Confounders"]

    node [shape=box, height=0.3, width=0.3]
    E [label="EDCs"]
    M [label="Glucocorticosteroids"]
    Y [label="HRT-SE"]
    { rank = same; E M}
